\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[small]{titlesec}
\usepackage{fullpage}
\usepackage{amsmath,amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{bbm}
\usepackage{comment}
\usepackage{subfiles}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{color}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{float}
\usepackage{xr-hyper}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}
\numberwithin{equation}{section}
\usepackage{float}


%\usepackage{bibtex}
%\usepackage[
 %   backend=biber,
 %   style=alphabetic,
 %   maxnames=50,
 %   firstinits=false,
 % ]{biblatex}

%\addbibresource{references.bib}

\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{assumption}[theorem]{Assumption}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\definecolor{brown}{rgb}{0.5, 0.21, 0.15}

\definecolor{darkgreen}{rgb}{0.05, 0.7, 0.06}
\newcommand{\brown}[1]{\textcolor{brown}{#1}}
\newcommand{\PM}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}} % \E abbreviation for expectation
\newcommand{\Log}{\operatorname{Log}}
\newcommand{\hol}{\mathrm{hol}}
\newcommand{\Ad}{\mathrm{Ad}}
\newcommand{\id}{\mathrm{id}}
\newcommand{\dif}{\,\mathrm{d}}
\newcommand{\diff}{\mathrm{d}}
\newcommand{\R}{\mathbb R}
\newcommand{\Law}{\mathrm{Law}}
\newcommand{\1}{\mathbf 1}
\newcommand{\<}{\langle}  
\renewcommand{\>}{\rangle}
\newcommand{\sign}{\operatorname{sgn}}

\newcommand{\hor}{\text{-}\mathrm{hor}}
\newcommand{\hgr}{\text{-}\mathrm{hgr}}
\newcommand{\ax}{\text{-}\mathrm{ax}}
\newcommand{\gr}{\text{-}\mathrm{gr}}



\definecolor{blueblue}{rgb}{0.3, 0.3, 0.95}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blueblue}{#1}}
\newcommand{\green}[1]{\textcolor{darkgreen}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}

\newcommand{\bfA}{\mathbf A}
\newcommand{\bA}{\mathbb A}
\newcommand{\bfOmega}{\boldsymbol{\Omega}}

\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cD}{\mathcal D}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cU}{\mathcal U}
\newcommand{\cX}{\mathcal X}
\newcommand{\cZ}{\mathcal Z}

\newcommand{\bHa}{\mathbb{H}_{\mathsf{a}}}
\newcommand{\bHc}{\mathbb{H}_{\mathsf{c}}}

\newcommand{\rmD}{\mathrm{D}}

\newcommand{\fG}{\mathfrak{G}}
\newcommand{\fg}{\mathfrak g}

\newcommand{\bC}{\mathbb C}
\newcommand{\T}{\mathbb T}
\newcommand{\bH}{\mathbb H}
\newcommand{\bN}{\mathbb N}
\newcommand{\bP}{\mathbb P}
\newcommand{\bQ}{\mathbb Q}
\newcommand{\bS}{\mathbb S}
\newcommand{\bT}{\mathbb T}
\newcommand{\bZ}{\mathbb Z}
\newcommand*\recvert[1]{\left[\!\left]#1\right[\!\right]}

\newcommand{\vertiii}[1]{{\left\vert\kern-0.4ex\left\vert\kern-0.4ex\left\vert #1 
    \right\vert\kern-0.4ex\right\vert\kern-0.4ex\right\vert}}
\newcommand{\triple}[1]{\vertiii{#1}}



    
%\title{Research Statement}
%\author{Abdulwahab Mohamed}
%\author{***}


\begin{document}

%\maketitle
\vspace{-10pt}
\begin{center}
    {\Large \textbf{Supporting Statement for Postdoctoral Position}} \\ \vspace{1pt}
    \textbf{Vacancy reference:} 176890\\
      Abdulwahab Mohamed \vspace{-0.5cm}
\end{center}

\section{Introduction}
My name is Abdulwahab Mohamed, and I am currently completing my PhD in Mathematics at the University of Edinburgh under the supervision of Dr.\ Ilya Chevyrev. Previously, I did my BSc and MSc at Eindhoven University of Technology. My research interests lie in stochastic analysis, particularly (singular) SPDEs and quantum gauge theory. 
%My PhD research aligns closely with the research focus of Prof.  Massimiliano Gubinelli. 
This supporting statement outlines how my background and experience fulfil the selection criteria for the postdoctoral position in Prof.\ Massimiliano Gubinelli's group. To ensure conciseness, the desirable selection criteria have been integrated into the essential selection criteria.

\section{Essential Selection Criteria}
\subsection{Have, or be close to completing, a PhD in Mathematics or Physics}
I am nearly completing my PhD in Mathematics at the University of Edinburgh, with my viva expected in July 2025. My PhD thesis focuses on problems in two-dimensional Yang-Mills theory, in particular rough Uhlenbeck compactness, as well as exploring an operator approach to Yang-Mills theory.

\subsection{Possess sufficient specialist knowledge in the discipline to work within established research programmes}

My research has required understanding and learning a recent field within stochastic analysis, namely rough analysis, particularly frameworks such as regularity structures and paracontrolled calculus to study singular SPDEs.  Moreover, the operator approach gave me an opportunity to revise elements from functional analysis, e.g., unbounded operators and spectral theory.

Additionally, I participated in a reading group on the flow equation approach organised by Prof.\ Nicolas Perkowski at FU Berlin, where I presented a section. This experience provided insight into recent methodologies in constructive QFT, such as renormalisation group methods. This complements my MSc thesis which focused on the multimarginal Schrödinger problem. That is a stochastic control problem which is relevant to some approaches in probabilistic QFT that Prof. Gubinelli has pioneered, e.g. in the paper ``A variational method for $\Phi^4_3$".

Hence this shows my experience in some of the topics mentioned in the desirable criteria, like constructive QFT, renormalisation group methods (e.g. flow equation approach), and singular SPDEs.


\subsection{Have the ability to manage own academic research and associated activities}
Throughout my PhD, I have independently managed many aspects of my research, from setting up problems to developing rigorous mathematical proofs. I have initiated a programme that significantly strengthened the main result in my main project on rough Uhlenbeck compactness. In there, there is an auxiliary singular SPDE which we solve using regularity structures and as such requires constructing singular objects. While normally one uses stochastic estimates to construct these singular objects, I realised that it should be possible to bypass stochastic estimates. 
%This belief is strengthened by my supervisor's work  "Yang-Mills measure on the two-dimensional torus as a random distribution," where a related result was achieved under less restrictive assumptions. 
With a lot of effort, I have managed to construct the singular objects through a much simpler and natural object called rough additive functions. This result, which even surprised my supervisor, highlights my ability to independently formulate and solve challenging problems.

Moreover, my independence has extended to initiating collaborations with researchers and contributing to the activities of research groups. For example, I initiated side projects with other PhD students on regularisation by noise for infinite-dimensional equations, including exploring extensions of the stochastic sewing methods. Although these projects did not lead to publications, they deepened my appreciation of the challenges involved in extending stochastic sewing techniques to infinite-dimensional settings. Additionally, I organised two reading groups—one on Malliavin calculus and the other on rough paths with applications to machine learning. These reading groups aimed to build a community of PhD students with shared interests in probability and analysis. 

\subsection{Previous experience of contributing to publications/presentations, with a strong publication track record for career stage}
I have presented my work at young researchers' meetings and workshops, including several invited presentations, as well as seminars. Although I have not yet published any papers, the novelties and techniques developed in my research are expected to yield a strong publication in a good journal.

\subsection{Possess the ability to contribute ideas for new research projects}
My main project, as mentioned before, requires solving a singular SPDE. This SPDE is auxiliary and there is a huge flexibility in setting up the equation. I  derived a suitable equation that allows to prove the relevant properties, allowing the project to progress after being stalled. To strengthen the main result, I introduced a `cosmetic' Da-Prato Debussche trick  with a non-standard Picard iteration and  a systematic framework for handling the singular objects. Additionally, I have introduced auxiliary objects to handle boundary regularity issues.  This is an idea whose usefulness I want to explore in different equations with boundary conditions as it would have push rough analysis ideas even further.

In the operator approach project, I quickly proved new results, including the Polishness of the gauge orbit space using resolvent estimates and a characterisation of gauge transformations via gauge-invariant observables. These contributions illustrate my ability to obtain ideas for new research projects.

\subsection{Excellent communication skills, including the ability to write for publication, present research proposals and results, and represent the research group at meetings}

I have trained my communication skills through teaching and giving talks in workshops and reading groups. I have experience leading tutorials at the University of Edinburgh and Eindhoven University of Technology, covering courses like calculus, probability, and advanced postgraduate topics. At Eindhoven, I contributed to developing learning materials by writing scripts for educational videos to make postgraduate probability theory more accessible. I also voluntarily organised one-day workshops for calculus exam preparation at Eindhoven University of Technology, gathering exercises and addressing common mistakes to support students. These workshops were well-received, with students appreciating the clarity and structure provided to help them prepare for  the exam.

The academic talks I have given have been well-received, and I have incorporated constructive feedback to improve future talks. For instance, my supervisor once advised me to choose the technical details in my talks based on the audience, as different aspects of my work interests different people. This advice has improved my ability to present my research to different types of audiences. 

Finally, during my studies at Eindhoven, I continuously trained my writing skills through coursework involving modelling components and technical reports.  I wrote the initial draft of the paper on rough Uhlenbeck compactness, demonstrating my ability to write research papers for publication. With feedback from my supervisor and collaborator, I am revising the paper to enhance its readability and structure.

I enjoy communicating and discussing mathematics and am happy to participate actively in the activities of the Stochastic Analysis research group and take on mentorship or teaching responsibilities as needed.


\section{Conclusion}
I am excited about the opportunity to be part of Prof. Gubinelli's research group. I believe that my expertise, skills, and experience align well with the group's objectives. I look forward to contributing actively to the group’s research and activities, including exploring new directions such as conformal field theory.


\end{document}


