\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[small]{titlesec}
\usepackage{fullpage}
\usepackage{amsmath,amsthm}
\usepackage{amssymb}
\usepackage{comment}
\usepackage{subfiles}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{color}
\usepackage{xcolor}
\usepackage{float}
\usepackage{xr-hyper}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}
\numberwithin{equation}{section}
\usepackage{float}


\definecolor{brown}{rgb}{0.5, 0.21, 0.15}

\definecolor{darkgreen}{rgb}{0.05, 0.7, 0.06}
\newcommand{\brown}[1]{\textcolor{brown}{#1}}


\definecolor{blueblue}{rgb}{0.3, 0.3, 0.95}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blueblue}{#1}}
\newcommand{\green}[1]{\textcolor{darkgreen}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}



    
\title{Interview Questions}
\author{Abdulwahab Mohamed}
%\author{***}


\begin{document}

\begin{center}
    {\Large \textbf{General Interview Questions}} \\ \vspace{1pt}
\end{center}

\section{Research-Focused Questions}
\begin{enumerate}
    \item Can you elaborate on your research background and how it aligns with our group's focus?
    
    \textit{Approach: Provide a concise overview of your research, emphasizing areas that intersect with the group's interests. Highlight specific projects or publications that demonstrate this alignment.}

    \item How do you envision contributing to our current projects, and what unique perspectives can you bring?
    
    \textit{Approach: Identify ongoing projects within the group and articulate how your expertise can enhance these endeavors. Propose potential research directions or methodologies that could be beneficial.}

    \item Describe a challenging problem you've encountered in your research and the steps you took to address it.
    
    \textit{Approach: Select a specific challenge, detail your problem-solving process, and reflect on the outcome and lessons learned.}

    \item How do you plan to build upon your PhD research in this postdoctoral role?
    
    \textit{Approach: Discuss how your doctoral work serves as a foundation and outline the specific directions you'd like to explore further.}

    \item What is the most significant open problem in your field, and how might your research contribute to solving it?
    
    \textit{Approach: Identify an open problem relevant to their group and propose your approach or ideas.}

    \item Can you compare different approaches to handling singularities in SPDEs?
    
    \textit{Approach: Highlight key methods and their trade-offs.}

    \item If given full autonomy, what research question would you tackle first, and why?
    
    \textit{Approach: Show initiative and originality.}

    \item Tell us about your previous research.
    
    \textit{Approach: Summarize your prior research succinctly, emphasizing key findings and methodologies.}

    \item Tell us about the work you would plan to do during this postdoc.
    
    \textit{Approach: Outline your planned research directions, linking them to the group's focus and goals.}

    \item Why is your work important/useful/relevant?
    
    \textit{Approach: Explain the broader significance and potential applications of your research.}

    \item What’s your dream theorem to prove in the next 3-5 years?
    
    \textit{Approach: Articulate an ambitious yet feasible goal that aligns with your expertise and field trends.}

    \item What’s something not in your area that you are interested in, and why?
    
    \textit{Approach: Highlight a curiosity or interdisciplinary interest, connecting it to your main research.}

    \item What would you like to learn?
    
    \textit{Approach: Reflect on skills or knowledge that would enhance your research capabilities or broaden your expertise.}


        \item \red{(From Tom)} Timeliness of research? - ongoing work in related areas?
    
    \textit{Approach: Discuss how your research fits into current trends and the broader context of the field.}

    \item \red{(From Tom)} What do you consider your most important/influential scientific contribution? Can you describe it first to a (lay person / undergraduate / expert)?
    
    \textit{Approach: Prepare tiered explanations of your work tailored to different audiences, emphasizing its impact and relevance.}

    \item \red{(From Tom)} Interest for communities outside your exact current area?
    
    \textit{Approach: Reflect on interdisciplinary applications of your work and how it might benefit adjacent fields.}

    \item \red{(From Tom)} What to do if projects are not successful?
    
    \textit{Approach: Share a strategy for adapting and learning from setbacks, including pivoting to new directions or revising approaches.}

    \item \red{(From Tom)} What are the most important open problems/big research challenges in your field?
    
    \textit{Approach: Identify key questions and articulate your perspective on their significance and potential solutions.}

    \item \red{(From Tom)} Who is doing the most interesting work in your area?
    
    \textit{Approach: Demonstrate knowledge of leading researchers and their contributions, highlighting collaborations or influences.}

    \item \red{(From Tom)} What are the big changes you expect to see in your area over the next decade?
    
    \textit{Approach: Discuss emerging trends and how they might reshape the field.}

    \item \red{(From Tom)} Does your work have links to machine learning/data science?
    
    \textit{Approach: Highlight any connections, such as methodologies or potential applications, between your research and these areas.}

    \item \red{(From Tom)} Who would you want to invite for seminars?
    
    \textit{Approach: Suggest researchers whose work complements or enriches the group’s focus, explaining your choices.}

    \item \red{(From Tom)} Which other institutions/departments would you want to reach out to or collaborate with? How?
    
    \textit{Approach: Outline potential partnerships and the mutual benefits of such collaborations.}

    
\end{enumerate}

\section{Collaboration and Teaching Questions}
\begin{enumerate}
    \item How have you collaborated with other researchers in the past, and what was the outcome?
    
    \textit{Approach: Highlight a specific collaboration, emphasizing your role and the results.}

    \item Are you comfortable mentoring graduate students or contributing to group teaching activities?
    
    \textit{Approach: Discuss past experiences and your willingness to engage with junior researchers.}

    \item How would you handle conflicts or differing opinions within a research group?
    
    \textit{Approach: Stress your ability to listen and mediate.}

    \item What collaborations do you have planned for this postdoc? (internal and external).
    
    \textit{Approach: Discuss potential collaborations, emphasizing how they align with the group’s work.}
\end{enumerate}

\section{Technical and Hypothetical Questions}
\begin{enumerate}
    \item How would you approach proving global existence or uniqueness for a challenging stochastic equation?
    
    \textit{Approach: Outline your strategy, referencing known methods while showing creativity in adapting them to new problems.}

    \item How would you explain the concept of rough paths to someone outside the field?
    
    \textit{Approach: Simplify the concept while retaining its mathematical essence.}

    \item What would you do if you encountered a significant gap in a proof during your research?
    
    \textit{Approach: Describe your process for addressing such challenges.}

    \item Imagine you are working on a collaborative project and hit a mathematical dead end. What steps would you take?
    
    \textit{Approach: Emphasize persistence and collaboration.}

    \item How would you address a scenario where the stochastic term in a PDE is irregular beyond the scope of current regularity structures?
    
    \textit{Approach: Suggest innovative approaches or adaptations.}

    \item How would you approach deriving a priori estimates for a specific PDE or SPDE?
    
    \textit{Approach: Walk through your strategy step-by-step.}

    \item What numerical methods have you used for solving PDEs or SPDEs?
    
    \textit{Approach: Explain your experience with computational tools.}
\end{enumerate}

\section{Broader Perspective Questions}
\begin{enumerate}
    \item How do you stay informed about the latest developments in stochastic analysis and related fields?
    
    \textit{Approach: Discuss your strategies for keeping up-to-date, such as attending conferences, participating in seminars, and engaging with recent literature.}

    \item What do you think are the most exciting developments in stochastic analysis or PDEs in recent years?
    
    \textit{Approach: Demonstrate awareness of the field by mentioning specific breakthroughs.}

    \item Where do you see your research fitting into the broader context of mathematics or applied sciences?
    
    \textit{Approach: Show how your work has broader implications.}

    \item How do you see stochastic analysis impacting other fields of mathematics or science?
    
    \textit{Approach: Highlight interdisciplinary connections.}

    \item How would you explain the significance of your work to a non-specialist audience?
    
    \textit{Approach: Simplify without losing depth.}

    \item What connections do you see between your work and Felix Otto’s contributions to optimal transport theory?
    
    \textit{Approach: Find links between your expertise and their work.}
\end{enumerate}

\section{Career and Motivation Questions}
\begin{enumerate}
    \item What are your long-term research goals, and how does this postdoctoral position fit into them?
    
    \textit{Approach: Outline your research aspirations and explain how the position at MPI Leipzig will facilitate achieving them.}

    \item Why did you choose this postdoc at MPI Leipzig?
    
    \textit{Approach: Be specific about the group’s reputation and how it aligns with your goals.}

    \item How do you plan to measure your success during your postdoc?
    
    \textit{Approach: Highlight clear goals and metrics.}

    \item What do you hope to achieve during your postdoc?
    
    \textit{Approach: Outline specific goals and outcomes you aim for.}

    \item What are your long-term career aspirations?
    
    \textit{Approach: Show ambition while remaining grounded.}

    \item What is the purpose of this postdoc for you?
    
    \textit{Approach: Reflect on how this position aligns with your research and career trajectory.}
\end{enumerate}

\section{Soft Skills and Non-Research Skills}
\begin{enumerate}
    \item What organizational experience do you have?
    
    \textit{Approach: Highlight instances where you demonstrated leadership, coordination, or event planning.}

    \item EDI: What is a problem that early career researchers face? What can the mathematical community do to help combat it?
    
    \textit{Approach: Reflect on challenges like funding, representation, or mentorship, and propose actionable solutions.}

    \item Tell us about a time you experienced a setback.
    
    \textit{Approach: Share a specific example, focusing on how you overcame the challenge and what you learned.}

    \item What are your strengths and weaknesses?
    
    \textit{Approach: Be honest, highlighting how you manage weaknesses and leverage strengths.}

    \item How would your advisor describe you?
    
    \textit{Approach: Reflect on feedback or comments you’ve received from mentors.}

    \item What are your back-up plans?
    
    \textit{Approach: Outline alternative career paths or research directions you’re prepared to pursue.}
\end{enumerate}

\section{Questions for the Interviewers}
\subsection{Research Opportunities and Group Dynamics}
\begin{enumerate}
    \item How does the group encourage collaboration among researchers with diverse expertise?

    \item Are there opportunities to co-supervise graduate students or participate in joint projects?

    \item How is feedback typically provided on ongoing research projects within the group?
\end{enumerate}

\subsection{Career Development}
\begin{enumerate}
    \item Are there formal mentoring or career development programs for postdocs?

    \item What are typical next steps for postdocs in your group after completing their term?
\end{enumerate}

\subsection{Resources and Support}
\begin{enumerate}
    \item Are there resources available for developing computational tools or accessing specific datasets?

    \item How much flexibility do postdocs have in proposing and pursuing independent projects?

    \item Will there be funding for research visits and conferences? (How much?)
\end{enumerate}

\subsection{Institutional Involvement}
\begin{enumerate}
    \item Are there opportunities to participate in interdisciplinary collaborations with other MPI groups or institutions?

    \item Does MPI Leipzig provide access to workshops, conferences, or training programs for skill development?
\end{enumerate}

\subsection{Group Vision and Expectations}
\begin{enumerate}
    \item What are the group’s priorities or focus areas for the next few years?

    \item How is the balance maintained between theoretical work and applications within the group?

    \item When is the expected start date?
\end{enumerate}


\section{Questions from Tom}

\subsection{Personal}
\begin{enumerate}
    \item Where do you see yourself in 5 years?
    
    \textit{Approach: Reflect on your career trajectory and articulate specific goals, such as positions, research achievements, or collaborations.}

    \item What do you want to be known for in 5 years' time?
    
    \textit{Approach: Highlight the unique contributions or areas of expertise you aim to establish in your field.}
\end{enumerate}



\subsection{Funding}
\begin{enumerate}
    \item What grants are you thinking of applying for? (less relevant for temporary posts)
    
    \textit{Approach: Discuss funding opportunities aligned with your research and your experience with proposal writing.}

    \item Projects that you would like to fund? (ditto)
    
    \textit{Approach: Highlight potential research areas that would benefit from additional funding, emphasizing their impact.}

    \item Experience applying for funding?
    
    \textit{Approach: Share examples of successful applications or insights gained from the process.}

    \item Do you think you would like to lead a research group in the near future? If so, what size? (X \# PhDs, Y \# postdocs.) (similar to career trajectory questions above)
    
    \textit{Approach: Articulate your vision for a research group, focusing on structure, goals, and collaboration.}
\end{enumerate}

\subsection{Teaching and Supervision}
\begin{enumerate}
    \item Teaching/supervision style/philosophy (even for temporary posts you may be called upon to teach or supervise BSc/MSc students)
    
    \textit{Approach: Describe your approach to mentoring and engaging students, focusing on inclusivity and active learning.}

    \item How to ensure students from diverse backgrounds are included?
    
    \textit{Approach: Highlight strategies for creating an inclusive environment that supports diverse learning needs.}

    \item Supervision experience?
    
    \textit{Approach: Share examples of past mentoring or supervision roles and the outcomes achieved.}

    \item Novel ways to teach students?
    
    \textit{Approach: Propose innovative teaching methods or tools you’ve used or plan to implement.}

    \item Courses you would like/be happy to teach (good idea to research the courses offered at the department but also less relevant for temporary posts)
    
    \textit{Approach: Suggest courses aligned with your expertise and the department’s curriculum.}

    \item Experience teaching?
    
    \textit{Approach: Discuss your teaching background, emphasizing methods that have been effective.}

    \item What would be your first project for a PhD student?
    
    \textit{Approach: Describe a feasible and meaningful project that aligns with your research goals.}

    \item If you had a PhD student/postdoc to work for you for the next three years, what would you get them to do? (again less relevant for temporary posts)
    
    \textit{Approach: Outline long-term projects that align with your vision and provide developmental opportunities for the student/postdoc.}

    \item What project would you give a master's student?
    
    \textit{Approach: Suggest a project scope suitable for a master’s level, balancing challenge and achievability.}

    \item What would you do if a Master's project turned out to be too challenging?
    
    \textit{Approach: Discuss strategies to reassess and adapt the project or provide additional support to the student.}

    \item What do you think are the qualities of a good PhD supervisor?
    
    \textit{Approach: Highlight traits like mentorship, clear communication, and adaptability, supported by examples.}
\end{enumerate}

\subsection{University}
\begin{enumerate}
    \item Why are you applying to ...? What attracts you here and why is now a good time to be here? (Almost always gets asked and very relevant for temporary posts)
    
    \textit{Approach: Discuss specific aspects of the institution and department that align with your goals and values.}

    \item Collaboration inside and outside the math department?
    
    \textit{Approach: Highlight potential interdisciplinary connections and collaborative opportunities.}

    \item Contribution to ...? What new will you bring to the department?
    
    \textit{Approach: Articulate unique skills, perspectives, or initiatives you can contribute.}

    \item Administration (or "service") is part of all academic life. Do you have experience with admin roles in the past? What roles do you see yourself in here? What outside of research and teaching would you bring to the department? (again more for permanent posts)
    
    \textit{Approach: Reflect on past administrative roles and how they prepared you for potential responsibilities.}

    \item Have you heard about our institute (...)? (e.g. INI, or ICMS, or Bayes Center, ...) Do you see yourself becoming involved in it?
    
    \textit{Approach: Express interest in the institute’s activities and potential contributions you could make.}

    \item Is there anyone in the department you would like to work or discuss with? (except the proposed project PI)
    
    \textit{Approach: Highlight researchers whose work you admire and explain potential synergies.}

    \item Also a good idea to write down some questions you would like to ask about the department/the role.
    
    \textit{Approach: Prepare thoughtful questions that demonstrate your interest and help clarify expectations.}
\end{enumerate}

\subsection{Questions Specifically for Abdul}
\subsubsection{Research-Related Questions}
\begin{enumerate}
    \item We have skimmed the working version of your project that you talked about and we have seen that you have been working on the document for quite a while. Could you please explain to us what major roadblocks you encountered that resulted in the project becoming quite long?
    
    \textit{Approach: Identify specific challenges and explain how you addressed them, emphasizing persistence and learning.}

    \item Which result within your current body of work are you most proud of and why?
    
    \textit{Approach: Share a result that highlights your skills and its broader impact.}

    \item The focus in your PhD, as we understand it, has been on Yang–Mills theory and its connections to rough paths theory and regularity structures. As you know, the focus of research in Leipzig is a bit less on mathematical physics. So which areas of overlap do you see with the topics represented here? Which people could you see yourself working with except the proposed project PI?
    
    \textit{Approach: Discuss interdisciplinary connections and potential collaborations within the department.}

    \item What is the most interesting development in your area of research at the moment?
    
    \textit{Approach: Highlight cutting-edge developments and their implications for your work.}

    \item Which are the most important open questions in the field?
    
    \textit{Approach: Identify key challenges and explain their importance to advancing the field.}
\end{enumerate}

\subsubsection{Personal Questions}
\begin{enumerate}
    \item Why are you applying to Leipzig? What attracts you here and why is now a good time to be here?
    
    \textit{Approach: Highlight specific aspects of Leipzig and its research environment that align with your goals.}

    \item There is a very lively seminar activity here in Leipzig. If you were in charge of organising the seminar, who would you invite?
    
    \textit{Approach: Suggest speakers whose work complements or enriches the group’s focus, explaining your choices.}

    \item The position we are currently interviewing you for is temporary. What is the plan after that? Where do you see yourself in, say, 5 years time?
    
    \textit{Approach: Share your long-term career vision and how this role fits into it.}

    \item Do you have any questions?
    
    \textit{Approach: Prepare thoughtful questions that show genuine interest in the role and research environment.}

    \item If we were to offer you a position, when would you be able to commit and when would you be able to start?
    
    \textit{Approach: Provide clear timelines, showing enthusiasm and flexibility.}
\end{enumerate}

\end{document}