\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[small]{titlesec}
\usepackage{fullpage}
\usepackage{amsmath,amsthm}
\usepackage{amssymb}
\usepackage{comment}
\usepackage{subfiles}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{color}
\usepackage{xcolor}
\usepackage{float}
\usepackage{xr-hyper}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}
\numberwithin{equation}{section}
\usepackage{float}


\definecolor{brown}{rgb}{0.5, 0.21, 0.15}

\definecolor{darkgreen}{rgb}{0.05, 0.7, 0.06}
\newcommand{\brown}[1]{\textcolor{brown}{#1}}


\definecolor{blueblue}{rgb}{0.3, 0.3, 0.95}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blueblue}{#1}}
\newcommand{\green}[1]{\textcolor{darkgreen}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}



    
\title{Interview Questions}
\author{Abdulwahab Mohamed}
%\author{***}


\begin{document}

\begin{center}
    {\Large \textbf{Interview Questions from Tom}} \\ \vspace{1pt}
\end{center}


\section{Questions from Tom}

\subsection{Personal}
\begin{enumerate}
    \item Where do you see yourself in 5 years?
    
    \textit{Approach: Reflect on your career trajectory and articulate specific goals, such as positions, research achievements, or collaborations.}

    \item What do you want to be known for in 5 years' time?
    
    \textit{Approach: Highlight the unique contributions or areas of expertise you aim to establish in your field.}
\end{enumerate}

\subsection{Research}
\begin{enumerate}
    \item Timeliness of research? - ongoing work in related areas?
    
    \textit{Approach: Discuss how your research fits into current trends and the broader context of the field.}

    \item What do you consider your most important/influential scientific contribution? Can you describe it first to a (lay person / undergraduate / expert)?
    
    \textit{Approach: Prepare tiered explanations of your work tailored to different audiences, emphasizing its impact and relevance.}

    \item Interest for communities outside your exact current area?
    
    \textit{Approach: Reflect on interdisciplinary applications of your work and how it might benefit adjacent fields.}

    \item What to do if projects are not successful?
    
    \textit{Approach: Share a strategy for adapting and learning from setbacks, including pivoting to new directions or revising approaches.}

    \item What are the most important open problems/big research challenges in your field?
    
    \textit{Approach: Identify key questions and articulate your perspective on their significance and potential solutions.}

    \item Who is doing the most interesting work in your area?
    
    \textit{Approach: Demonstrate knowledge of leading researchers and their contributions, highlighting collaborations or influences.}

    \item What are the big changes you expect to see in your area over the next decade?
    
    \textit{Approach: Discuss emerging trends and how they might reshape the field.}

    \item Does your work have links to machine learning/data science?
    
    \textit{Approach: Highlight any connections, such as methodologies or potential applications, between your research and these areas.}

    \item Who would you want to invite for seminars?
    
    \textit{Approach: Suggest researchers whose work complements or enriches the group’s focus, explaining your choices.}

    \item Which other institutions/departments would you want to reach out to or collaborate with? How?
    
    \textit{Approach: Outline potential partnerships and the mutual benefits of such collaborations.}
\end{enumerate}

\subsection{Funding}
\begin{enumerate}
    \item What grants are you thinking of applying for? (less relevant for temporary posts)
    
    \textit{Approach: Discuss funding opportunities aligned with your research and your experience with proposal writing.}

    \item Projects that you would like to fund? (ditto)
    
    \textit{Approach: Highlight potential research areas that would benefit from additional funding, emphasizing their impact.}

    \item Experience applying for funding?
    
    \textit{Approach: Share examples of successful applications or insights gained from the process.}

    \item Do you think you would like to lead a research group in the near future? If so, what size? (X \# PhDs, Y \# postdocs.) (similar to career trajectory questions above)
    
    \textit{Approach: Articulate your vision for a research group, focusing on structure, goals, and collaboration.}
\end{enumerate}

\subsection{Teaching and Supervision}
\begin{enumerate}
    \item Teaching/supervision style/philosophy (even for temporary posts you may be called upon to teach or supervise BSc/MSc students)
    
    \textit{Approach: Describe your approach to mentoring and engaging students, focusing on inclusivity and active learning.}

    \item How to ensure students from diverse backgrounds are included?
    
    \textit{Approach: Highlight strategies for creating an inclusive environment that supports diverse learning needs.}

    \item Supervision experience?
    
    \textit{Approach: Share examples of past mentoring or supervision roles and the outcomes achieved.}

    \item Novel ways to teach students?
    
    \textit{Approach: Propose innovative teaching methods or tools you’ve used or plan to implement.}

    \item Courses you would like/be happy to teach (good idea to research the courses offered at the department but also less relevant for temporary posts)
    
    \textit{Approach: Suggest courses aligned with your expertise and the department’s curriculum.}

    \item Experience teaching?
    
    \textit{Approach: Discuss your teaching background, emphasizing methods that have been effective.}

    \item What would be your first project for a PhD student?
    
    \textit{Approach: Describe a feasible and meaningful project that aligns with your research goals.}

    \item If you had a PhD student/postdoc to work for you for the next three years, what would you get them to do? (again less relevant for temporary posts)
    
    \textit{Approach: Outline long-term projects that align with your vision and provide developmental opportunities for the student/postdoc.}

    \item What project would you give a master's student?
    
    \textit{Approach: Suggest a project scope suitable for a master’s level, balancing challenge and achievability.}

    \item What would you do if a Master's project turned out to be too challenging?
    
    \textit{Approach: Discuss strategies to reassess and adapt the project or provide additional support to the student.}

    \item What do you think are the qualities of a good PhD supervisor?
    
    \textit{Approach: Highlight traits like mentorship, clear communication, and adaptability, supported by examples.}
\end{enumerate}

\subsection{University}
\begin{enumerate}
    \item Why are you applying to ...? What attracts you here and why is now a good time to be here? (Almost always gets asked and very relevant for temporary posts)
    
    \textit{Approach: Discuss specific aspects of the institution and department that align with your goals and values.}

    \item Collaboration inside and outside the math department?
    
    \textit{Approach: Highlight potential interdisciplinary connections and collaborative opportunities.}

    \item Contribution to ...? What new will you bring to the department?
    
    \textit{Approach: Articulate unique skills, perspectives, or initiatives you can contribute.}

    \item Administration (or "service") is part of all academic life. Do you have experience with admin roles in the past? What roles do you see yourself in here? What outside of research and teaching would you bring to the department? (again more for permanent posts)
    
    \textit{Approach: Reflect on past administrative roles and how they prepared you for potential responsibilities.}

    \item Have you heard about our institute (...)? (e.g. INI, or ICMS, or Bayes Center, ...) Do you see yourself becoming involved in it?
    
    \textit{Approach: Express interest in the institute’s activities and potential contributions you could make.}

    \item Is there anyone in the department you would like to work or discuss with? (except the proposed project PI)
    
    \textit{Approach: Highlight researchers whose work you admire and explain potential synergies.}

    \item Also a good idea to write down some questions you would like to ask about the department/the role.
    
    \textit{Approach: Prepare thoughtful questions that demonstrate your interest and help clarify expectations.}
\end{enumerate}

\subsection{Questions Specifically for Abdul}
\subsubsection{Research-Related Questions}
\begin{enumerate}
    \item We have skimmed the working version of your project that you talked about and we have seen that you have been working on the document for quite a while. Could you please explain to us what major roadblocks you encountered that resulted in the project becoming quite long?
    
    \textit{Approach: Identify specific challenges and explain how you addressed them, emphasizing persistence and learning.}

    \item Which result within your current body of work are you most proud of and why?
    
    \textit{Approach: Share a result that highlights your skills and its broader impact.}

    \item The focus in your PhD, as we understand it, has been on Yang–Mills theory and its connections to rough paths theory and regularity structures. As you know, the focus of research in Leipzig is a bit less on mathematical physics. So which areas of overlap do you see with the topics represented here? Which people could you see yourself working with except the proposed project PI?
    
    \textit{Approach: Discuss interdisciplinary connections and potential collaborations within the department.}

    \item What is the most interesting development in your area of research at the moment?
    
    \textit{Approach: Highlight cutting-edge developments and their implications for your work.}

    \item Which are the most important open questions in the field?
    
    \textit{Approach: Identify key challenges and explain their importance to advancing the field.}
\end{enumerate}

\subsubsection{Personal Questions}
\begin{enumerate}
    \item Why are you applying to Leipzig? What attracts you here and why is now a good time to be here?
    
    \textit{Approach: Highlight specific aspects of Leipzig and its research environment that align with your goals.}

    \item There is a very lively seminar activity here in Leipzig. If you were in charge of organising the seminar, who would you invite?
    
    \textit{Approach: Suggest speakers whose work complements or enriches the group’s focus, explaining your choices.}

    \item The position we are currently interviewing you for is temporary. What is the plan after that? Where do you see yourself in, say, 5 years time?
    
    \textit{Approach: Share your long-term career vision and how this role fits into it.}

    \item Do you have any questions?
    
    \textit{Approach: Prepare thoughtful questions that show genuine interest in the role and research environment.}

    \item If we were to offer you a position, when would you be able to commit and when would you be able to start?
    
    \textit{Approach: Provide clear timelines, showing enthusiasm and flexibility.}
\end{enumerate}

\end{document}